Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-08-23 Paper/Paper.tex

\begin{figure}[ht!]
    \centering
    \captionsetup{width=.7\linewidth}
    \caption{Hospital EHR Adoption Over Time}
    \includegraphics[scale=.7]{Objects/hosp_treat.pdf}
    \label{fig:hosp_treat}
\end{figure}

@@

This outcome, total patient count, is directly related to the fraction of patients seen in an office setting. For younger physicians, since the total number of patients increases in the first couple of years after exposure, the absolute number of patients seen in offices increases as well. That is, it seems that younger physicians are shifting a positive amount of work towards offices but still able to increase productivity in the time spent in the hospital, thus the null effect on fraction of office patients.

>>>>

\begin{figure}[ht!]
    \centering
    \captionsetup{width=.7\linewidth}
    \caption{Hospital EHR Adoption Over Time}
    \includegraphics[scale=.5]{Objects/hosp_treat.pdf}
    \label{fig:hosp_treat}
\end{figure}

@@

Since I found in the earlier stages of analysis that physicians may have shifted away from hospitals due to EHR exposure, I also investigate whether this increase in the number of patients seen is due to the decrease in working physicians. For example, if a hospital loses a portion of their physicians, they may divide that physician's patients between the remaining physicians. In the long run, the hospital should hire new physicians to replace those that left, but if this does not happen right away my results could be driven by the retiring physicians instead of EHR use. In Figure

\begin{figure}[ht]
    \centering
    \captionsetup{width=.85\linewidth}
    \caption{Effect of EHR Exposure on Claim Count}
    \includegraphics[scale=.6]{Objects/number.pdf}
    \label{fig:claim}
    \vspace{2mm}
    \caption*{\footnotesize{\textit{Notes:} The top panel shows average group time treatment effects aggregated over groups to an event study plot. The bottom show these results for different subgroups of physicians by age. The p-value listed for each graph corresponds to a Wald test for pre-trends. Confidence intervals shown are simultaneous confidence bands accounting for multiple hypothesis testing. Overall ATT for all, $<$ 60, $>=$ 60 with SE in parentheses: 4.04 (33.89), 25.77 (31.26), -161.06 (133.35), respectively.}}
\end{figure}
